Language-Based Security for Low-Level MPC

### 2024-09-03 ppdp24/slides.tex
checkpoint

\begin{frame}{(Passive) Threat Model}
  The adversary wants to guess secrets. In addition to knowing the public
  output, the adversary may also corrupt \emph{any} subset of clients $C$:
  \begin{itemize}
  \item adversary has access to the secrets of clients in $C$.
  \item adversary has access to messages received by members of $C$ during execution of $\prog$,
    aka \cemph{adversarial views}.
  \end{itemize}

@@

  To implement 3-party summation (xor in $\mathbb{F}_2$), we can use \emph{Shamir addition}.
  Each party first generates \emph{reconstructive shares}.

  \begin{block}{Reconstructive Sharing}
    $$
    \begin{array}{lll}
      \elab{\mesg{s1}}{2} &:=& \elab{(\secret{1} \fminus \locflip \fminus \flip{x})}{1} \\ 
      \elab{\mesg{s1}}{3} &:=& \elab{\flip{x}}{1} \\ 
      \elab{\mesg{s2}}{1} &:=& \elab{(\secret{2} \fminus \locflip \fminus \flip{x})}{2} \\ 
      \elab{\mesg{s2}}{3} &:=& \elab{\flip{x}}{2} \\ 
      \elab{\mesg{s3}}{1} &:=& \elab{(\secret{3} \fminus \locflip \fminus \flip{x})}{3} \\ 
      \elab{\mesg{s3}}{2} &:=& \elab{\flip{x}}{3}
    \end{array}
    $$
  \end{block}
  \begin{itemize}
  \item \emph{algebraically} we have $\elab{\mesg{s1}}{2} + \elab{\mesg{s1}}{3} + \elab{\locflip}{1}$, etc.
  \item \emph{probabilistically} any 2 out of three shares are in a uniform random distribution.
  \end{itemize}

@@

  \begin{exampleblock}{2-Party GMW (Contd.)}

>>>>

\begin{frame}{(Passive) Threat Model}
  The adversary wants to guess secrets. In addition to knowing the public
  output, the adversary may also corrupt \emph{any} subset of clients $C$:
  \begin{itemize}
  \item adversary has access to the secrets of clients in $C$.
  \item adversary has access to messages received by members of $C$ during execution of $\prog$,
    aka \cemph{adversarial views}.
  \item adversary cannot break the rules of the protol\footnote{Malicious security also
  considered separately in our work.}.
  \end{itemize}

@@

  To implement 3-party summation in any $\mathbb{F}_p$, we can use \emph{Shamir addition}.
  Each party first generates \emph{reconstructive shares}.

  \begin{block}{Reconstructive Sharing}
    $$
    \begin{array}{lll}
      \elab{\mesg{s1}}{2} &:=& \elab{(\secret{1} \fminus \locflip \fminus \flip{x})}{1} \\ 
      \elab{\mesg{s1}}{3} &:=& \elab{\flip{x}}{1} \\ 
      \elab{\mesg{s2}}{1} &:=& \elab{(\secret{2} \fminus \locflip \fminus \flip{x})}{2} \\ 
      \elab{\mesg{s2}}{3} &:=& \elab{\flip{x}}{2} \\ 
      \elab{\mesg{s3}}{1} &:=& \elab{(\secret{3} \fminus \locflip \fminus \flip{x})}{3} \\ 
      \elab{\mesg{s3}}{2} &:=& \elab{\flip{x}}{3}
    \end{array}
    $$
  \end{block}
  \begin{itemize}
  \item $\elab{\mesg{s1}}{2}, \elab{\mesg{s1}}{3}, \elab{\locflip}{1}$ are the \emph{shares} of $\sx{1}{1}$,
    etc.
  \item \emph{algebraically} $\sx{1}{1} = \elab{\mesg{s1}}{2} + \elab{\mesg{s1}}{3} + \elab{\locflip}{1}$.
  \item \emph{probabilistically} any 2 out of three shares are in a uniform random distribution.
  \end{itemize}

@@

  \begin{exampleblock}{Semi-Automatically Verifying 2-Party GMW}
